Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-18 mplr-2021/programming21-reviews-answered.txt

Said that for Globtoregexp.I__opts already!

> Fig 3: Why not depict the example extraction step --- which sometimes
> includes manual addition of examples --- here? And consider
> representing Jalangi's role in this architecture.

Fernando?

> Sec 4.2/4.3: As mentioned, I think a lot more detail is warranted
> about the instrumentation and the process for computing types from
> traces.
> 
> "Execution of Code Examples": Interesting to see how many examples
> were perhaps out-of-date or were not proper examples. Were there any
> interesting patterns worth discussing?
> 
> p.17: It's encouraging to see how the proposed tool can fix some
> errors found in manual type declarations!
> 
> "Literal types vs string": If considering asking developers to mark
> strings, instead why not ask them to directly use, e.g. the "Enums" or
> "Discriminated Unions" (https://www.typescriptlang.org/docs/handbook)?
> 
> "Any": Ditto above; why not ask developers to choose the any type?
> 
> "Further types": Inferring indexed types, dependent types, etc. from
> run-time traces would seem to require quite significant technical
> extensions to the approach described here.
> 
> TSInfer: Is it fundamental that TSInfer apparently generates
> signatures for helpers? Could there not be a simple syntactic analysis
> that identifies top-level definitions, to be include in a declaration
> file?
> 
> 
> *** Minor Comments and Typos ***
> 
> Fig 1: Maybe I'm missing it, but I don't see Footnote 6 anywhere.j
> 
> p.5: "globToRegexp" ==> "GlobToRegexp" twice
> 
> p.8: I'm not sure why "syntax highlighting is done correctly" is
> noteworthy here.
> 
> Fig 4: Is this referenced in the text?
> 
> p.15: "loose" ==> "lose"
>

DONE.

### 2021-05-20 mplr-2021/main.tex
snapshot

As \texttt{dts-generate} is based on run-time information, 
exemplary code fragments that execute the JavaScript library are
needed to obtain 
significant run-time information from running the instrumented library
code.

>>>>

As \texttt{dts-generate} is based on run-time information, code
fragments are needed that import and use the JavaScript library to
obtain run-time information from running the instrumented library
code.
